[dcpo_demsupport] Appendix

### 2020-08-04 paper/dcpo_demsupport.Rmd

```{r dcpo-uncertainty, cache=TRUE}
# Preload function ----
vcovBK_se <- function(x) {
  vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

@@

load(here::here("data", "dcpo_input.rda"))
load(here::here("data", "dcpo_theta.rda"))

@@

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    pdata.frame(index = c("country", "year"))
})

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
        plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) +
        plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset
  )
})

>>>>

```{r dcpo-uncertainty, cache=TRUE}
# Preload function ----
vcovBK_se <- function(x) {
  plm::vcovBK(x, cluster = "time") %>% 
    diag() %>% 
    sqrt()
}

@@

load(here::here("data", "dcpo_theta.rda"))

@@

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
        plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) +
        plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset)
})

### 2020-08-04 paper/dcpo_demsupport_appendix.Rmd

df_thetaDraw <- map_df(seq(ls_year), # year2
                       function(oneYear) {
                         map_df(seq(ls_country),
                                function(oneCountry) {
                                  df_temp <-
                                    sample(claassen_m5_theta$theta[, oneYear, oneCountry],
                                           size = 100, #draw 100 from the distribution
                                           replace = TRUE) %>%
                                    matrix(ncol = 100) %>%
                                    as_tibble()
                                  df_temp$year <- ls_year[oneYear]
                                  df_temp$country <- ls_country[oneCountry]
                                  return(df_temp)
                                })
                       }) %>% 
  pivot_longer(
    cols = starts_with("V"),
    names_to = "draw",
    values_to = "theta"
  ) %>% 
  group_split(draw)

df_controls <- read_csv(here::here("data", "Support_democracy_ajps.csv"),
                        col_types = cols(
                          .default = col_double(),
                          Country = col_character(),
                          Cnt_code = col_character(),
                          ISO_code = col_character(),
                          Region_UN = col_character()))

df_thetaDraw <- map(df_thetaDraw, function(oneDraw){
  left_join(oneDraw, df_controls, by = c("country" = "Country", "year" = "Year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_m5O <- plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(SupDem_trim, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), pdata.frame(df_controls, index = c("Country", "Year")), model="pooling")

result_m5N <- map(df_thetaDraw, function(aDataset){
  plm(Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + plm::lag(theta, 1) + plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1), model="pooling", data = aDataset)
})

@@

result_betas_m5 <- mitools::MIextract(result_m5N, fun = coef)
result_vars_m5 <- mitools::MIextract(result_m5N, fun = vcovBK_se)

summary(result_m5O)
summary(mitools::MIcombine(results = result_betas_m5, 
                           variance = result_vars_m5))

@@

summary(mitools::MIcombine(results = result_betas_m5_1k, 
                           variance = result_vars_m5_1k))
```

>>>>

@@

@@

df_result_cls <- summary(mitools::MIcombine(results = result_betas_m5_1k, variance = result_vars_m5_1k))%>% rownames_to_column(var = "term") %>% 
  rename(conf.low = `(lower`,
         conf.high = `upper)`, 
         estimate = results) %>% 
  filter(!str_detect(term, "(Intercept)"))
```

```{r dcpoVisualization, fig.cap= "Replication of Model 5 in Claassen's AJPS 2019"}

(dwplot(df_result_cls, by_2sd = FALSE)) %>% 
  relabel_predictors(c(`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)", #there's a lag in the replication file
`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)")) +
  geom_vline(xintercept = 0, colour = "grey80", linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") + 
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank(),
        legend.position = "none")
